---
title: "Mapping the Landscape of Precision Public Health: A Bibliometric Analysis of Influential Works and Key Contributors" 
author:
  - name: Mohd Azmi Bin Suliman
    orcid: 0000-0002-2125-3811
    affiliation: Institut Kesihatan Umum
  - name: Tham Sin Wan
    orcid: 0000-0002-5925-3200
    affiliation: Institut Kesihatan Umum
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format:
  docx:
    df-print: kable
    toc: true
    dpi: 320
  html:
    theme: flatly
    code-fold: show
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: kable
    embed-resources: true
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    fontsize: .9em
    monofont: 'Fira Code'
---

# Setup

## Library & Setup

```{r}
pacman::p_load(tidyverse, bibliometrix, stringi, 
               kableExtra, summarytools)

bibds_wos_por <- read_csv("240419_bibds_wos_postor.csv")
```

# Introduction

# Methodology

## Data Source & Inclusion Criteria

-   Database: Web of Science Core Collection, which include
    -   A&HCI: Arts & Humanities Citation Index
    -   ESCI: Emerging Sources Citation Index
    -   SCI-EXPANDED: Science Citation Index Expanded
    -   SSCI: Social Sciences Citation Index
-   Date Access: 19/04/2024
-   Search Term: TS=("public health precision") OR TS=("precision public health")
    -   TS: Topic, which include Title, Abstract and Author's Keywords
    -   TI: Title
    -   link: https://www.webofscience.com/wos/woscc/summary/4e07b2e9-e0db-4bff-ac3d-f09a49adaed7-e0a53927/relevance/1

## Data Analysis

-   Software
    -   R
    -   RStudio
    -   Bibliometrix
-   Parameters
    -   Production by Year
    -   Influential Articles
    -   Influential Authors
    -   Influential Journals
    -   Influential Keywords

# Results

## Production by Year

```{r}
bibds_wos_por %>%
  count(PY) %>%
  ggplot(aes(x = PY, y = n)) + 
  geom_col() + 
  scale_x_continuous(breaks = seq(2000, 2030, 1), 
                     name = "Year") + 
  scale_y_continuous(breaks = seq(0, 50, 5), 
                     name = "Number of Publication") +
  theme_bw()
```

## Influential Articles

### Total Cited

```{r}
bibds_wos_por %>% 
  select(TI, AU, TC, DI) %>% 
  arrange(desc(TC)) %>% 
  mutate(Rank = row_number(), .before = 1) %>% 
  filter(Rank < 11)
```

### Total Cited per Year

```{r}
bibds_wos_por %>% 
  select(TI, AU, DI, PY, TC) %>% 
  mutate(dur = 2024 - PY + 1,
         tcy = TC / dur) %>% 
  arrange(desc(tcy)) %>% 
  mutate(Rank = row_number(), .before = 1) %>% 
  filter(Rank < 11)
```

## Influential Authors

```{r}
bibds_wos_por %>% 
  select(AU) %>% 
  separate_longer_delim(AU, ";") %>% 
  count(AU) %>% 
  arrange(desc(n), AU) %>%
  filter(n > 4) %>% 
  mutate(Rank = row_number(), .before = 1)
```

## Influential Journals

### Top Journals

```{r}
bibds_wos_por %>% 
  count(SO) %>% 
  arrange(desc(n), SO) %>% 
  mutate(Rank = row_number(), .before = 1) %>% 
  filter(n > 2) 
```

### Bradford's Law

Bradford's law stated that, in a given subject area, a small number of journals account for a sizeable portion of the total publications in that area, whereas increasing numbers of journals publish fewer articles in that area.

It can be group into 3 zone, with core zone is the smallest number of journals that account for the largest number of articles.

```{r}
bibds_wos_por %>% 
  count(SO) %>% 
  arrange(desc(n), SO) %>% 
  mutate(sum_n = cumsum(n)) %>% 
  mutate(Rank = row_number(), .before = 1) %>% 
  filter(sum_n <= sum(n) / 3 + 1)
```

## Influential Keywords

### Author's Keywords


```{r}
bibds_wos_por %>% 
  select(DE) %>% 
  separate_longer_delim(DE, ";") %>% 
  count(DE) %>% 
  arrange(desc(n), DE) %>% 
  filter(n > 6) %>% 
  mutate(Rank = row_number(), .before = 1)
```


### WOS Keywords

```{r}
bibds_wos_por %>% 
  select(ID) %>%
  separate_longer_delim(ID, ";") %>%
  count(ID) %>%
  arrange(desc(n), ID) %>% 
  filter(n > 7) %>% 
  mutate(Rank = row_number(), .before = 1)
```

# Conclusion

-   The concept of Public Health Precision was quite recent, with the first publication in 2015.
-   The publication was increasing in the first 4 years, but later fluctuate in the final 4 years.
-   Several prominent authors, articles and journal were identified.
-   The concept of Public Health Precision was still growing and there is increasing interest in the topic.
