---
title: "2025 - Bibliometric Elderly Malnutrition"
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format: 
  html:
    theme: flatly
    code-fold: show
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: paged
    default-image-extension: svg
    embed-resources: true
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    fontsize: .9em
    monofont: 'Fira Code'
execute: 
  warning: false
number-sections: true
toc: true
fig-dpi: 320
dpi: 320
---

# Setup

```{r}
#| label: setup

pacman::p_load(tidyverse, bibliometrix, janitor, stringi, summarytools)
```

# Dataset

## Search Criteria

- Database: Web of Science
- Date: 08/04/2025
- Timespan: 1994-2023
- Type: Articles, Not Proceeding Paper, Book Chapter, Retracted Publication, Early Access, Withdrawn Publication
- Search Term:  

TI=("malnutrit*" OR "malnourish*" OR "poor nutrition" OR "undernutrit*" OR "nutrition* deficien*" OR "nutrition* status" OR "nutrition* disorder*" OR "micronutrient deficien*" OR "nutrition* health")  
AND  
TI=("elder*" OR "older adult*" OR "older person*" OR "older people*" OR "ageing" OR "geriatric*" OR "senior citizen*" OR "senior*")

Note: WOS unable to save more than 1000 records, thus require combine. combine using biblioshiny

## Load Dataset

```{r}
#| eval: false

biblioshiny()
```


```{r}
load("2025-04-08_ElderlyMalnutrition_Combine.RData")

eldmln_ds <- M %>% 
  filter(PY < 2024)

rm(M)
```

## Exploration

```{r}
dupti <- eldmln_ds %>% 
  count(TI, sort = T) %>% 
  filter(n > 1) %>% 
  pull(TI)

eldmln_ds %>% 
  arrange(TI, PY) %>% 
  filter(TI %in% dupti) %>% 
  mutate(ti_short = str_sub(TI, 1, 100), .before = 1)
```

```{r}
eldmln_ds %>% 
  count(PY)

eldmln_ds %>% 
  count(DT)
```

# Analysis

## Summary

```{r}
eldmln_bibres <- biblioAnalysis(eldmln_ds, sep = ";")

summary(eldmln_bibres)
```

# Authors

```{r}
eldmln_ds %>% 
  select(TI, PY, AF)
```

# Additional

```{r}
autime <- readxl::read_xlsx(
  "additional after shiny/AuthorProdTime_19942023.xlsx", 
  range = "A2:E127") %>% 
  group_by(Author, year) %>% 
  summarise(freq = sum(freq), 
            TC = sum(TC), 
            .groups = "drop")

autime

autime_wide <- autime %>% 
  select(-TC) %>% 
  arrange(year) %>% 
  pivot_wider(names_from = year, 
              values_from = freq, 
              values_fill = 0)

autime_wide
```

```{r}
# Step 1: Pivot to long format
autime_long <- autime_wide %>%
  pivot_longer(
    cols = -Author,
    names_to = "year",
    values_to = "freq"
  ) %>%
  mutate(
    year = as.integer(year),
    freq = as.integer(freq)
  )

# Step 2: Optional — reorder authors by total productivity
autime_long <- autime_long %>%
  group_by(Author) %>%
  mutate(total = sum(freq)) %>%
  ungroup() %>%
  mutate(Author = fct_reorder(Author, total))

# Step 3: Draw heatmap
ggplot(autime_long, aes(x = year, y = Author, fill = freq)) +
  geom_tile(color = "white") +
  scale_fill_gradientn(
    colours = c("white", "green", "red"),
    values = scales::rescale(c(0, 1, max(autime_long$freq))),
    name = "Publications"
  ) + 
  geom_vline(xintercept = c(2003.5, 2013.5), colour = "red") +
  labs(
    x = "Year",
    y = "Author",
    title = "Heatmap of Author Publications by Year"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.y = element_text(size = 8),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank()
  )

```

