---
title: "2025 - Bibliometric Elderly Malnutrition"
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format: 
  html:
    theme: flatly
    code-fold: show
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: paged
    default-image-extension: svg
    embed-resources: true
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    fontsize: .9em
    monofont: 'Fira Code'
execute: 
  warning: false
number-sections: true
toc: true
fig-dpi: 320
dpi: 320
---

# Setup

```{r}
pacman::p_load(tidyverse, bibliometrix, janitor, stringi, summarytools)
```

# Dataset

## Search Criteria

- Database: Web of Science
- Date: 08/04/2025
- Timespan: 1994-2023
- Type: Articles, Not Proceeding Paper, Book Chapter, Retracted Publication, Early Access, Withdrawn Publication
- Search Term:  

TI=("malnutrit*" OR "malnourish*" OR "poor nutrition" OR "undernutrit*" OR "nutrition* deficien*" OR "nutrition* status" OR "nutrition* disorder*" OR "micronutrient deficien*" OR "nutrition* health")  
AND  
TI=("elder*" OR "older adult*" OR "older person*" OR "older people*" OR "ageing" OR "geriatric*" OR "senior citizen*" OR "senior*")

Note: WOS unable to save more than 1000 records, thus require combine. combine using biblioshiny

## Load Dataset

```{r}
#| eval: false

biblioshiny()
```


```{r}
load("2025-04-08_ElderlyMalnutrition_Combine.RData")

eldmln_ds <- M %>% 
  filter(PY < 2024)

rm(M)
```

## Exploration

```{r}
dupti <- eldmln_ds %>% 
  count(TI, sort = T) %>% 
  filter(n > 1) %>% 
  pull(TI)

eldmln_ds %>% 
  arrange(TI, PY) %>% 
  filter(TI %in% dupti) %>% 
  mutate(ti_short = str_sub(TI, 1, 100), .before = 1)
```

```{r}
eldmln_ds %>% 
  count(PY)

eldmln_ds %>% 
  count(DT)
```

# Analysis

## Summary

```{r}
eldmln_bibres <- biblioAnalysis(eldmln_ds, sep = ";")

summary(eldmln_bibres)
```

# Authors

```{r}
eldmln_ds %>% 
  select(TI, PY, AF)
```

