---
title: "2025 - Bibliometric Childhood Obesity"
date: last-modified
date-format: "dddd, DD/MM/YYYY"
format: 
  html:
    theme: flatly
    code-fold: true
    code-copy: hover
    code-overflow: wrap
    code-tools: true
    df-print: paged
    default-image-extension: svg
    embed-resources: true
    page-layout: full
    reference-location: margin
    title-block-banner: true
    title-block-style: default
    fontsize: .9em
    monofont: 'Fira Code'
execute: 
  warning: false
number-sections: true
toc: true
fig-dpi: 320
dpi: 320
---

# Setup

```{r}
#| label: setup

pacman::p_load(tidyverse, googledrive, bibliometrix, janitor, stringi, 
               summarytools)
```

# Import Database and Export

## Search Criteria

- Database: Scopus
- Date Access: 23/02/2025
- Search Term: 

TITLE ( "pediatric" OR "paediatric" OR "childhood" OR "adolescent" OR "youth" ) AND TITLE ( "obesity" OR "obese" OR "overweight" ) AND PUBYEAR > 2003 AND PUBYEAR < 2024 AND ( LIMIT-TO ( DOCTYPE , "ar" ) ) AND ( LIMIT-TO ( PUBSTAGE , "final" ) ) AND ( LIMIT-TO ( SRCTYPE , "j" ) ) AND ( LIMIT-TO ( LANGUAGE , "English" ) )


## Import Database

```{r}
#| eval: false

pedob_bibds <- convert2df("250223_ScopusSearch.csv", 
                          dbsource = "scopus", 
                          format = "csv", 
                          remove.duplicates = TRUE)

head(pedob_bibds)

write_rds(pedob_bibds, "pedob_bibds.rds")
```


```{r}
pedob_bibds <- read_rds("pedob_bibds.rds")
```

## Explore

```{r}
dupti <- pedob_bibds %>% 
  count(TI, sort = T) %>% 
  filter(n > 1) %>% 
  pull(TI)

pedob_bibds %>% 
  arrange(TI, PY) %>% 
  filter(TI %in% dupti) %>% 
  mutate(ti_short = str_sub(TI, 1, 100), .before = 1)

```

there was however several with same title.


```{r}
pedob_bibds %>% 
  count(PY)
```

```{r}
pedob_bibds %>% 
  count(DT)
```

# Analysis

## Summary

```{r}
#| eval: false

pedob_bibres <- biblioAnalysis(pedob_bibds, sep = ";")

write_rds(pedob_bibres, "pedob_bibres.rds")
```

```{r}
pedob_bibres <- read_rds("pedob_bibres.rds")

summary(pedob_bibres)
```

## Production

### Summary

```{r}
pedob_bibds %>% 
  count(PY) %>% 
  mutate(Gap = case_when(
    PY %in% 1994:2003 ~ "1994-2003", 
    PY %in% 2004:2013 ~ "2004-2013", 
    PY %in% 2014:2023 ~ "2014-2023"
  )) %>% 
  group_by(Gap) %>% 
  summarise(n = sum(n), .groups = "drop") %>% 
  bind_rows(., 
            summarise(., Gap = "1994-2023 (total)", n = sum(n)))
```

### Trend

```{r}
gmagr_9423 <- pedob_bibds %>% 
  count(PY)  %>%
  mutate(AGR = (n - lag(n)) / lag(n) * 100) %>% 
  filter(!is.na(AGR)) %>% 
  summarise(geommean_agr = (exp(mean(log(1 + AGR / 100))) - 1) * 100) %>% 
  pull(geommean_agr)

gmagr_9423
```

```{r}
gmagr_9403 <- pedob_bibds %>% 
  count(PY)  %>% 
  filter(PY %in% 1994:2003) %>% 
  mutate(AGR = (n - lag(n)) / lag(n) * 100) %>% 
  filter(!is.na(AGR)) %>% 
  summarise(geommean_agr = (exp(mean(log(1 + AGR / 100))) - 1) * 100) %>% 
  pull(geommean_agr)

gmagr_9403
```

```{r}
gmagr_0413 <- pedob_bibds %>% 
  count(PY)  %>% 
  filter(PY %in% 2004:2013) %>% 
  mutate(AGR = (n - lag(n)) / lag(n) * 100) %>% 
  filter(!is.na(AGR)) %>% 
  summarise(geommean_agr = (exp(mean(log(1 + AGR / 100))) - 1) * 100) %>% 
  pull(geommean_agr)

gmagr_0413
```

```{r}
gmagr_1423 <- pedob_bibds %>% 
  count(PY)  %>% 
  filter(PY %in% 2014:2023) %>% 
  mutate(AGR = (n - lag(n)) / lag(n) * 100) %>% 
  filter(!is.na(AGR)) %>% 
  summarise(geommean_agr = (exp(mean(log(1 + AGR / 100))) - 1) * 100) %>% 
  pull(geommean_agr)

gmagr_1423
```

```{r}
#4682B4 steelblue
#CD5C5C indianred
#2E8B57 seagreen

pedob_bibds %>% 
  count(PY) %>% 
  ggplot(aes(x = PY, y = n)) + 
  geom_vline(xintercept = c(2003, 2013), 
             linetype = "dashed", colour = "indianred") + #CD5C5C
  geom_col(fill = "seagreen", colour = "black") + #2E8B57
  annotate("text", x = 2005, y = 1000, 
           label = paste0("1994-2023 AGR = ", 
                          sprintf("%.1f", gmagr_9423), "%"), 
           color = "black", hjust = 0, size = 3) +  # 1994-2023
  annotate("text", x = 1995, y = 200, 
           label = paste0("1994-2003 AGR = ", 
                          sprintf("%.1f", gmagr_9403), "%"), 
           color = "black", hjust = 0, size = 3) +  # 1994-2003
  annotate("text", x = 2005, y = 800, 
           label = paste0("2004-2013 AGR = ", 
                          sprintf("%.1f", gmagr_0413), "%"), 
           color = "black", hjust = 0, size = 3) +  # 2004-2013
  annotate("text", x = 2015, y = 900, 
           label = paste0("2014-2023 AGR = ", 
                          sprintf("%.1f", gmagr_1423), "%"), 
           color = "black", hjust = 0, size = 3) +  # 2014-2023
  scale_x_continuous(breaks = seq(1988, 2030, 5)) +
  scale_y_continuous(breaks = seq(0, 1100, 100)) + 
  coord_cartesian(ylim = c(0, 1050)) +
  labs(title = "Annual Publication Count",
       x = "Publication Year",
       y = "Number of Publications") +
  theme_bw()

```

## Journal

### Summary

```{r}
pedob_bibds %>% 
  summarise(total_unique_journals = n_distinct(SO))
```

```{r}
pedob_bibds %>% 
  count(SO, sort = T) %>% 
  slice_max(n, n = 20) %>% 
  mutate(rank = row_number(), .before = 1)
```

### Trend

```{r}
pedob_bibds %>% 
  filter(PY %in% 1994:2003) %>% 
  count(SO, sort = TRUE) %>% 
  slice_max(n, n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```

```{r}
pedob_bibds %>% 
  filter(PY %in% 2004:2013) %>% 
  count(SO, sort = TRUE) %>% 
  slice_max(n, n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```

```{r}
pedob_bibds %>% 
  filter(PY %in% 2014:2023) %>% 
  count(SO, sort = TRUE) %>% 
  slice_max(n, n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```

## Author

```{r}
oriau_byti0 <- pedob_bibds %>% 
  select(TI, PY, AF) %>% 
  separate_wider_delim(AF, delim = ";", names = paste0("af", 1:10), 
                       too_many = "drop", too_few = "align_start") %>% 
  pivot_longer(cols = starts_with("af"), 
               names_to = "author_position", 
               values_to = "au_nameid", values_drop_na = TRUE) %>% 
  mutate(au_nameid = str_trim(au_nameid),  
         au_name = str_extract(au_nameid, "^[^(]+"), 
         au_name = str_trim(au_name), 
         au_name = str_to_upper(au_name), 
         au_name = stri_trans_general(au_name, "Latin-ASCII"), 
         au_name = str_replace_all(au_name, "-", " "), 
         au_name = str_replace_all(au_name, ",", " "), 
         au_name = str_replace_all(au_name, "\\.", " "), 
         au_name = str_trim(au_name), 
         au_name = str_replace_all(au_name, "\\s+", " "), 
         au_scid = str_extract(au_nameid, "(?<=\\().+?(?=\\))")) %>% 
  arrange(au_scid)

oriau_byti0
```

```{r}
# Step 1: Standardized Name by Scopus ID (Preferring Longer Names)
stdname_list1 <- oriau_byti0 %>% 
  arrange(au_scid, desc(nchar(au_name)), PY, author_position) %>%  # Prefer longer names first
  group_by(au_scid) %>%
  summarise(std_name = first(au_name), .groups = "drop") %>% 
  arrange(desc(au_scid))  # Descending order by Scopus ID

# Step 2: Merge Standardized Name Back
oriau_byti1 <- oriau_byti0 %>% 
  left_join(stdname_list1, by = "au_scid")

# Step 3: Standardized Scopus ID by Standardized Name (Preferring Longer Names)
stdscid_list1 <- oriau_byti1 %>% 
  arrange(desc(nchar(std_name)), PY, author_position) %>%  # Prefer longer names
  group_by(std_name) %>% 
  summarise(std_scid = first(au_scid), .groups = "drop") %>% 
  arrange(desc(std_name))  # Descending order by name

# Step 4: Final Merge - Add Standardized Scopus IDs Back
oriau_byti2 <- oriau_byti1 %>% 
  left_join(stdscid_list1, by = "std_name")

oriau_byti2
```

```{r}
# Check for inconsistencies

oriau_byti2 %>% 
  count(std_name, std_scid) %>% 
  count(std_name) %>% filter(n > 1)

oriau_byti2 %>% 
  count(std_name, std_scid) %>% 
  count(std_scid) %>% filter(n > 1)
```

### Summary


```{r}
oriau_byti2 %>% 
  count(std_name, sort = T) %>% 
  slice_head(n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```

```{r}
oriau_byti2 %>% 
  filter(PY %in% 1994:2003) %>% 
  count(std_name, sort = T) %>% 
  slice_head(n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```

```{r}
oriau_byti2 %>% 
  filter(PY %in% 2004:2013) %>% 
  count(std_name, sort = T) %>% 
  slice_head(n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```

```{r}
oriau_byti2 %>% 
  filter(PY %in% 2014:2023) %>% 
  count(std_name, sort = T) %>% 
  slice_head(n = 10) %>% 
  mutate(rank = row_number(), .before = 1)
```


## Keywords

### Summary

```{r}
pedob_bibds %>% 
  mutate(keyword_count = str_count(DE, ";") + 1) %>% 
  count(keyword_count)
```

```{r}
#4682B4 steelblue
#CD5C5C indianred
#2E8B57 seagreen

pedob_bibds %>% 
  mutate(keyword_count = str_count(DE, ";") + 1) %>% 
  count(keyword_count) %>% 
  ggplot(aes(x = keyword_count, y = n)) + 
  geom_col(fill = "#2E8B57", color = "black") + # seagreen
  scale_x_continuous(breaks = seq(1, 21, 1)) + 
  scale_y_continuous(breaks = seq(0, 5000, 500)) + 
  coord_cartesian(xlim = c(1, 11)) + # there are papers with DE > 15!
  labs(title = "Number of Author's Keyword per Articles", 
       x = "Author's Keywords Count", 
       y = "Number of Publications") +
  theme_bw()
```

```{r}
debyti <- pedob_bibds %>% 
  select(TI, PY, DE) %>% 
  separate_wider_delim(DE, delim = ";", names = paste0("de", 1:10), 
                       too_many = "drop", too_few = "align_start") %>% 
  pivot_longer(cols = starts_with("de"), 
               names_to = "de_position", 
               values_to = "de_aukw", 
               values_drop_na = T) %>% 
  mutate(de_aukw = str_trim(de_aukw), 
         de_aukw = str_to_upper(de_aukw), 
         de_aukw = str_replace_all(de_aukw, "\\s+", " "), 
         de_aukw = str_replace_all(de_aukw, "-", " "), 
         de_aukw = stri_trans_general(de_aukw, "Latin-ASCII") )

debyti
```

```{r}
debyti %>% 
  count(de_aukw, sort = T) 
```

### Trend

```{r}
debyti %>% 
  filter(PY %in% 1994:2003) %>% 
  count(de_aukw, sort = T) 

debyti %>% 
  filter(PY %in% 2004:2013) %>% 
  count(de_aukw, sort = T) 

debyti %>% 
  filter(PY %in% 2014:2023) %>% 
  count(de_aukw, sort = T) 
```

